Formalizing Stack Safety as a Security Property

### 2021-07-07 submission3/main.tex
Answered BCP and APT as much as I could, and added forward pointer to callee-saves

\section{Key Concepts}
\label{sec:setup}

\bcp{I am having trouble deciding what this section should be called.
  Probably this means I don't really understand its purpose...}

@@

\section{Threat Model}
\label{sec:threat}

@@

@@

      Supporting a dynamic notion of adversary is important for
      functions that cannot be statically proven safe, but whose data
      still need to be protected when they are behaving safely.
      For example, consider a function that obeys the reasonableness
      constraints on most inputs, but can be subverted by malicious inputs
      in such a way that it violates the reasonableness constraints. In
      the StkTokens model, we cannot guarantee to protect this function's
      data from its callees even when it called with non-malicious inputs.
      \apt{too abstract now?}
%      \sna{TODO: expand}

\item Their approach to proving safety via fully abstract overlay
  semantics relies on the definition of a ``stack-safe-by-construction''
  abstract machine that is closely tied to the underlying actual
  machine architecture and and enforcement mechanism.
  %the the abstract machine being architecturally similar to
  %      the concrete one (beyond the specific call and return semantics that
  %      distinguish them).
  While the fundamental approach can no doubt be ported to other architectures and enforcement
  schemes, each such port requires a new abstract machine definition whose
  safe-by-construction character must be (informally) verified afresh.
  Our properties are more generic, and apply directly to a wide range of architectures,
  code features, and enforcement mechanisms.
  \apt{too strong? perhaps should (re-)enumerate what we need to adjust in each setting.}

>>>>

\section{Setting}
\label{sec:setup}

\bcp{I am having trouble deciding what this section should be called.
  Probably this means I don't really understand its purpose...}
\sna{Propose merging it with next section like so.}

@@

\paragraph*{Threat Model}
\label{sec:threat}

@@

Lazy policies are not the only scenario to call for a weaker property of this kind.
Some code features may involve moving data, overwriting its original location,
and ultimately restoring it before the change becomes visible; for example, the
``callee-saves'' registers in some calling conventions will be stashed and restored.
Stepwise stack safety can never support such a feature, but in section \ref{calleesave}
we show how {\em observational properties} can.

@@

      Supporting a dynamic notion of adversary is important for
      functions that cannot be statically proven safe, but whose data
      still need to be protected when they are behaving safely.
      For example, consider a function that obeys the reasonableness
      constraints on most inputs, but can be subverted by malicious inputs
      in such a way that it violates the reasonableness constraints. In
      the StkTokens model, we cannot guarantee to protect this function's
      data from its callees even when it called with non-malicious inputs.
      \apt{too abstract now?}
      \sna{Maybe, but I'm not sure how much being concrete about it serves us.}

\item Their approach to proving safety via fully abstract overlay
  semantics relies on the definition of a ``stack-safe-by-construction''
  abstract machine that is closely tied to the underlying actual
  machine architecture and and enforcement mechanism.
  %the the abstract machine being architecturally similar to
  %      the concrete one (beyond the specific call and return semantics that
  %      distinguish them).
  While the fundamental approach can no doubt be ported to other architectures and enforcement
  schemes, each such port requires a new abstract machine definition whose
  safe-by-construction character must be (informally) verified afresh.
  Our properties are more generic: since we abstract over most of the machine
  state as well as the sealing and return conventions, they apply directly
  to a range of architectures, code features, and enforcement mechanisms.

  Likewise, it would be possible to extend their abstract machine to pass arguments
  on the stack, or to support callee-save registers. It might even viable to
  construct a safe-by-construction abstract coroutine machine, but so far this is
  hypothetical. We implement these scenarios in fact, with simple modifications to
  the domain model of each one.
